The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-17 paper/ms.tex
phrasing

In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

@@

\begin{figure*}
\plotone{Pope_Fig8_v1.pdf}
\caption{\label{fig:ncap}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[blue circles][]{Battistini2016}. These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}

>>>>

In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.

@@

\begin{figure*}
\plotone{Pope_Fig8_v1.pdf}
\caption{\label{fig:ncap}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[red,][]{Bensby2014}, \citet[blue][]{Battistini2016}. These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}
